\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{placeins}
\usepackage{hyperref}
\geometry{margin=1in}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{criterion}[theorem]{Criterion}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\rad}{rad}
\newcommand{\vp}{v_p}
\newcommand{\vq}{v_q}
\newcommand{\OPN}{\mathrm{OPN}}
\newcommand{\PhiD}{\Phi_d}
\newcommand{\Lset}{\mathcal L}
\newcommand{\B}{\mathcal B}
\newcommand{\K}{\mathcal K}
\newcommand{\Hfun}{H}
\newcommand{\CertRelease}{\ensuremath{\mathcal C^{(2026\text{-}07)}_{5,7,11,13,17}}}
\newcommand{\Csmall}{\ensuremath{\mathcal C_{\mathrm{small}}}}
\newcommand{\sha}[1]{\nolinkurl{#1}}
\newcommand{\shasplit}[2]{\begin{tabular}[t]{@{}l@{}}{\ttfamily\tiny #1}\\[-1pt]{\ttfamily\tiny #2}\end{tabular}}
\urlstyle{same}

\title{Certified Minimal-Prime Branch Closures for Odd Perfect Numbers}
\author{
Marco Mantovanelli\\
Independent Researcher\\[0.5em]
\texttt{marco@mantovanelli.de}
}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Let \(N\) be a hypothetical odd perfect number and let
\(q=\min\{p:p\mid N\}\) be its smallest prime divisor.  This paper isolates
the certified minimal-prime part of a broader cyclotomic-certificate framework.
It proves, within the frozen certificate release \(\Csmall\), that the branch
inventories for \(q=5,7,11,13,17\) are exhausted.  The result is deliberately
not stated as an unconditional
nonexistence proof for odd perfect numbers: the structurally exceptional branch
\(q=3\) and the residual branch \(q\ge19\) remain outside the scope of this
paper.  The main text gives the branch definitions, valuation balance,
coverage splits, certificate contract, and one closure theorem per branch.
Detailed JSONL archives, large finite tables, and verifier outputs are kept as
separate machine-readable certificates.
\end{abstract}

\noindent\textbf{Keywords.}
Odd perfect numbers; divisor sums; cyclotomic factors; \(p\)-adic valuations;
minimal prime divisor; branch-and-bound certification; computer-assisted proof.

\smallskip

\noindent\textbf{MSC 2020.}
Primary 11A25; Secondary 11Y05, 11Y16.

\section{Introduction}

An odd perfect number is a positive odd integer \(N\) satisfying
\[
  \sigma(N)=2N,
\]
where \(\sigma\) denotes the sum of divisors.  The existence of odd perfect
numbers is one of the classical open problems in number theory; Deza's book
\cite{Deza2022} gives a broad account of the surrounding perfect-number and
amicable-number landscape.  Euler proved that any such \(N\) has the form
\[
  N=\pi^\alpha M^2,\qquad
  \pi\equiv \alpha\equiv1\pmod4,\qquad (\pi,M)=1,
\]
so exactly one prime divisor of \(N\), called the Euler prime, occurs to an odd
exponent.

The modern literature supplies strong global filters, but not a complete
nonexistence proof.  Nielsen proved that every odd perfect number has at least
nine distinct prime factors and later developed related Diophantine and
upper-bound methods \cite{Nielsen2007,Nielsen2015}.  Ochem and Rao proved the
landmark lower bound \(N>10^{1500}\) and strong multiplicity constraints
\cite{OchemRao2012}.
Goto--Ohno and Iannucci established large-prime-factor lower bounds
\cite{GotoOhno2008,Iannucci1999,Iannucci2000}.  More recent work of Zelinsky,
Bibby--Vyncke--Zelinsky, Clayton--Hansen, and Stone gives further constraints
on prime counts, largest prime factors, reciprocal abundance, and
smallest-prime behavior
\cite{Zelinsky2019,Zelinsky2021,Zelinsky2023SmallPrimes,
BibbyVynckeZelinsky2021,ClaytonHansen2023,Stone2024,
Zelinsky2025ReciprocalPrimeDivisors}.  The present paper uses these results
only as branch filters and consistency checks; the actual branch closures below
are driven by valuation-labeled cyclotomic input and finite certificates.

The present paper concerns only a finite list of minimal-prime branches.  Write
\(S=\{p:p\mid N\}\), \(q=\min S\), and
\(N=\prod_{p\in S}p^{e_p}\).  Thus the branch \(q=5\), for example, means that
\(5\mid N\) and \(3\nmid N\), not merely that \(5\mid N\).

The main theorem proved here is the following certificate theorem.

\begin{theorem}[Certified small minimal-prime closure]
\label{thm:intro-main}
Relative to the explicitly listed verifier contract and the frozen certificate
release \(\Csmall\) described in Section~\ref{sec:certificates}, there is
no odd perfect number with \(\min\{p:p\mid N\}\in\{5,7,11,13,17\}\).
Equivalently, the five minimal-prime branch inventories in \(\Csmall\)
are exhausted.
\end{theorem}

The theorem is intentionally scoped.  It is not an unconditional proof that odd
perfect numbers do not exist.  After the certified closures in this paper, a
complete proof program must still treat \(q=3\) and \(q\ge19\).
The branch \(q=3\) has no lower-prime avoidance layer and therefore behaves
differently from all branches treated here.  The residual branch \(q\ge19\)
should be attacked only after the small-prime branch architecture has been made
fully proof-grade.

\section{Minimal-Prime Branches and Scope}
\label{sec:scope}

\begin{definition}[Minimal-prime branch]
\label{def:minimal-prime-branch}
Let \(q\) be an odd prime.  The minimal-prime branch \(\B_q\) is the set of all
formal odd-perfect-number realizations satisfying
\[
  q=\min\{p:p\mid N\}.
\]
Thus \(q\in S\), all odd primes \(\ell<q\) are absent from \(S\), and every
branch calculation is carried out under Euler's form and the equation
\(\sigma(N)=2N\).
\end{definition}

\begin{definition}[Frozen certificate release]
\label{def:frozen-certificate-release}
The symbol \(\CertRelease\) denotes the July 2026 release of the five small
minimal-prime certificate packages used in this paper.  It consists of the
bundle files, verifier files, expected terminal outputs, and SHA256 hashes
listed in the reproducibility table in Section~\ref{sec:certificates}.  The
word ``release'' is meant literally: the proof statements below are relative to
these frozen files, not to whatever local working copy may exist later.  For
readability, after this definition we also write \(\Csmall := \CertRelease\).
\end{definition}

\begin{definition}[Release branch inventory]
\label{def:release-branch-inventory}
For \(q=5,7,11,13,17\), the \emph{\(\Csmall\)-branch inventory} is the
finite, machine-readable collection of coverage splits, forced cofactors,
leaf-status records, tail certificates, pure-exception records, and master
coverage wrappers listed in the release JSONL certificate files.  A branch is
called \emph{closed relative to \(\Csmall\)} when every leaf in that
inventory is certified as refuted, forced-tail-controlled, pure-tail-controlled,
or delegated to a certified child archive, and when the master wrapper verifies
that the listed leaves cover the parent branch.
\end{definition}

\begin{remark}[Scope warning]
\label{rem:scope-warning}
Every closure theorem below is a minimal-prime theorem.  The statement
``the \(q=11\) branch is closed'' means
\[
  \min\{p:p\mid N\}=11
\]
has no realization in the certified branch inventory.  It does not assert that
no odd perfect number can be divisible by \(11\); it excludes only the case in
which \(11\) is the smallest prime divisor.
\end{remark}

\section{Valuation Balance}
\label{sec:valuation-balance}

The branch closures are driven by local valuations of divisor sums.

\begin{lemma}[Odd-prime valuation balance]
\label{lem:odd-prime-valuation-balance}
Let \(N=\prod_{p\in S}p^{e_p}\) be an odd perfect number, and let \(q\) be an
odd prime.  If \(q\mid N\), then
\[
  e_q
  =
  \sum_{\substack{p\in S\\p\ne q}}
  v_q(\sigma(p^{e_p})).
\]
If \(q\nmid N\), then
\[
  \sum_{p\in S}v_q(\sigma(p^{e_p}))=0.
\]
\end{lemma}

\begin{proof}
By multiplicativity of \(\sigma\) and by \(\sigma(N)=2N\),
\[
  v_q(\sigma(N))=v_q(2N)=v_q(N)
\]
for odd \(q\).  If \(q\mid N\), this value is \(e_q\).  The factor
\(\sigma(q^{e_q})=1+q+\cdots+q^{e_q}\) is congruent to \(1\pmod q\), so it
contributes no \(q\)-adic valuation.  This gives the first identity.  If
\(q\nmid N\), the right side is \(v_q(2N)=0\); since each summand is
nonnegative, all summands vanish.
\end{proof}

\begin{lemma}[Cyclotomic input condition]
\label{lem:cyclotomic-input-condition}
Let \(p\ne q\) be primes with \(q\) odd, and let \(e\ge0\).  Put
\[
  n=e+1,\qquad d=\ord_q(p).
\]
Then
\[
  v_q(\sigma(p^e))
  =
  \begin{cases}
  0, & d\nmid n,\\[3pt]
  v_q(p^d-1)+v_q(n/d), & d>1\text{ and }d\mid n,\\[3pt]
  v_q(n), & d=1.
  \end{cases}
\]
In particular,
\[
  q\mid \sigma(p^e)
  \quad\Longleftrightarrow\quad
  \begin{cases}
  d\mid e+1, & d>1,\\
  q\mid e+1, & d=1.
  \end{cases}
\]
\end{lemma}

\begin{proof}
Since
\[
  \sigma(p^e)=\frac{p^{e+1}-1}{p-1},
\]
we have
\[
  v_q(\sigma(p^e))=v_q(p^n-1)-v_q(p-1).
\]
If \(d\nmid n\), then \(p^n\not\equiv1\pmod q\), hence the valuation is zero.
If \(d>1\) and \(d\mid n\), write \(n=dm\).  Then \(q\nmid p-1\), and LTE gives
\[
  v_q(p^n-1)=v_q((p^d)^m-1)=v_q(p^d-1)+v_q(m).
\]
If \(d=1\), then \(p\equiv1\pmod q\), and LTE gives
\[
  v_q(p^n-1)=v_q(p-1)+v_q(n).
\]
Subtracting \(v_q(p-1)\) proves the formula.
\end{proof}

The exact formula of Bordelles \cite{Bordelles2026} gives a published
valuation-level check for this same local rule, while the Ross--Shen--Cai
Lucas-sequence valuation formula \cite{RossShenCai2025} gives an independent
check for the cyclotomic labels \(v_r(\Phi_d(p))\).  The certificate system
uses direct factorization and order checks, with these published formulas as
the theorem-level background.

\section{Lower-Prime Avoidance}
\label{sec:lower-prime-avoidance}

\begin{definition}[Lower-prime set and avoidance predicate]
For an odd prime \(q\), define
\[
  \Lset(q):=\{\ell:\ell\text{ is an odd prime and }\ell<q\}.
\]
For an odd prime \(\ell\), a prime \(p\ne\ell\), and \(e\ge1\), define
\[
  \operatorname{Avoid}_{\ell}(p,e)
\]
to mean
\[
  \begin{cases}
  \ord_\ell(p)\nmid e+1, & \ord_\ell(p)>1,\\[3pt]
  \ell\nmid e+1, & \ord_\ell(p)=1.
  \end{cases}
\]
By Lemma~\ref{lem:cyclotomic-input-condition}, this is equivalent to
\[
  v_\ell(\sigma(p^e))=0.
\]
\end{definition}

\begin{lemma}[Lower-prime avoidance]
\label{lem:lower-prime-avoidance}
Assume \(N\) is an odd perfect number and \(q=\min S\).  Then for every
\(\ell\in\Lset(q)\) and every \(p\in S\),
\[
  v_\ell(\sigma(p^{e_p}))=0.
\]
Equivalently,
\[
  \operatorname{Avoid}_{\ell}(p,e_p)
\]
holds for all \(\ell<q\) and all support primes \(p\).
\end{lemma}

\begin{proof}
Let \(\ell<q=\min S\).  Then \(\ell\notin S\), so \(\ell\nmid N\).  Applying
Lemma~\ref{lem:odd-prime-valuation-balance} to \(\ell\) gives
\[
  \sum_{p\in S}v_\ell(\sigma(p^{e_p}))=0.
\]
Each summand is nonnegative, and therefore every summand is zero.  The
equivalence with \(\operatorname{Avoid}_{\ell}\) is exactly
Lemma~\ref{lem:cyclotomic-input-condition}.
\end{proof}

\begin{table}[ht]
\centering
\begin{tabular}{c|l}
\toprule
branch \(q=\min S\) & lower primes avoided by every support prime power \\
\midrule
\(5\) & \(3\)\\
\(7\) & \(3,5\)\\
\(11\) & \(3,5,7\)\\
\(13\) & \(3,5,7,11\)\\
\(17\) & \(3,5,7,11,13\)\\
\bottomrule
\end{tabular}
\caption{Lower-prime avoidance constraints used in this paper.}
\label{tab:lower-prime-avoidance}
\end{table}

\begin{corollary}[Support floors from excluded small primes]
\label{cor:support-floors}
In the minimal-prime branches treated here, the active published lower bound
for the number of distinct prime divisors is
\[
\begin{array}{c|c}
q & \text{active lower bound for }\omega(N)\\
\hline
5,7 & 12,\\
11,13,17 & 27.
\end{array}
\]
\end{corollary}

\begin{proof}
If \(q=5\) or \(q=7\), then \(3\nmid N\), so Nielsen's lower bound in the
form surveyed by Deza \cite{Deza2022,Nielsen2007} gives
\(\omega(N)\ge12\).  If \(q\ge11\), then \(3,5,7\nmid N\); the same
Deza--Nielsen sources record the corresponding small-prime-exclusion form,
which gives \(\omega(N)\ge27\) in this situation.
\end{proof}

\section{Input Orders and Coverage Splits}
\label{sec:coverage}

\begin{definition}[\(q\)-input witness]
In the branch \(q=\min S\), a prime \(p\in S\), \(p\ne q\), is a
\(q\)-input witness if
\[
  v_q(\sigma(p^{e_p}))>0.
\]
Its order type is \(d=\ord_q(p)\).
\end{definition}

\begin{lemma}[Existence of a \(q\)-input witness]
\label{lem:q-input-exists}
Let \(q=\min S\).  Then at least one \(q\)-input witness exists.
\end{lemma}

\begin{proof}
Since \(q\in S\), we have \(e_q>0\).  The \(q\)-adic balance gives
\[
  e_q=\sum_{\substack{p\in S\\p\ne q}}v_q(\sigma(p^{e_p})).
\]
The right side is a sum of nonnegative integers and is positive.  Hence at
least one summand is positive.
\end{proof}

\begin{lemma}[Allowed input orders]
\label{lem:allowed-input-orders}
Let \(q\) be one of \(5,7,11,13,17\), and let \(p\ne q\) be a \(q\)-input
witness.  If \(p\) is non-Euler, then \(\ord_q(p)\) is an odd divisor of
\(q-1\).  If \(p=\pi\) is the Euler prime, then \(\ord_q(\pi)\mid q-1\) and
\[
  v_2(\ord_q(\pi))\le1.
\]
\end{lemma}

\begin{proof}
By Lemma~\ref{lem:cyclotomic-input-condition}, either \(\ord_q(p)\mid e_p+1\)
or, in the order-one case, \(q\mid e_p+1\).  For non-Euler \(p\), Euler's form
gives \(e_p\) even, so \(e_p+1\) is odd; hence only odd orders can divide it.
For the Euler prime, \(\alpha\equiv1\pmod4\), so \(\alpha+1\equiv2\pmod4\);
therefore no divisor of \(\alpha+1\) is divisible by \(4\).  In all cases the
order divides \(q-1\).
\end{proof}

\begin{table}[ht]
\centering
\small
\begin{tabular}{c|l|l}
\toprule
\(q\) & non-Euler input children & Euler input children\\
\midrule
\(5\)  & \(N_1\) & \(E_1,E_2\)\\
\(7\)  & \(N_1,N_3\) & \(E_1,E_2,E_3,E_6\)\\
\(11\) & \(N_1,N_5\) & \(E_1,E_2,E_5,E_{10}\)\\
\(13\) & \(N_1,N_3\) & \(E_1,E_2,E_3,E_6\)\\
\(17\) & \(N_1\) & \(E_1,E_2\)\\
\bottomrule
\end{tabular}
\caption{First-input coverage labels.  \(N_d\) means a non-Euler
\(q\)-input witness of exact order \(d\) modulo \(q\); \(E_d\) means the Euler
prime is a \(q\)-input witness of exact order \(d\).}
\label{tab:first-input-labels}
\end{table}

\begin{proposition}[Coverage split for \(q=5,7,11,13,17\)]
\label{prop:general-coverage-split}
For each \(q\in\{5,7,11,13,17\}\), every hypothetical odd perfect number in the
minimal-prime branch \(q=\min S\) realizes at least one child listed in
Table~\ref{tab:first-input-labels}.
\end{proposition}

\begin{proof}
By Lemma~\ref{lem:q-input-exists}, a \(q\)-input witness exists.  If the
witness is non-Euler, Lemma~\ref{lem:allowed-input-orders} restricts its order
to the odd divisors of \(q-1\), giving exactly the \(N_d\)-labels in
Table~\ref{tab:first-input-labels}.  If the witness is the Euler prime, the
same lemma restricts the order to those divisors of \(q-1\) not divisible by
\(4\), giving exactly the \(E_d\)-labels in the table.  The split is a coverage
split, not necessarily a disjoint split: a single branch could contain several
input witnesses.
\end{proof}

\section{Reduced Cofactors and Pure Exceptions}
\label{sec:cofactors}

The first-input splits produce cyclotomic factors dividing one of the
divisor-sum terms \(\sigma(x^{e_x})\).  After removing the contribution of the
minimal prime \(q\), the remaining cofactor either has a lower-prime divisor,
has a new forced support prime, or falls into a pure exceptional row.

\begin{definition}[Reduced cofactor]
\label{def:reduced-cofactor}
Let \(q=\min S\), and let \(x\) be a \(q\)-input source of order \(d\).
For \(d>1\), the reduced cofactor is the corresponding cyclotomic factor
\[
  C_d^{(q)}(x)
  :=
  \frac{\Phi_d(x)}{q^{v_q(\Phi_d(x))}}.
\]
For order-one input, the first nontrivial \(q\)-cyclotomic cofactor is
\[
  C_q(x):=\frac{\Phi_q(x)}{q}.
\]
For Euler order-two input, the reduced linear cofactor is
\[
  C_2^{(q)}(\pi):=\frac{\pi+1}{q^{v_q(\pi+1)}}.
\]
When \(q=17\), the certificate records the odd part of this cofactor for the
forced-prime alternative, and records the remaining power-of-two case as a pure
row.
\end{definition}

\begin{lemma}[Forced-prime alternative]
\label{lem:forced-prime-alternative}
Let \(q=\min S\), and suppose a reduced cofactor \(C\) divides
\(\sigma(x^{e_x})\).  If \(C\) has an odd prime divisor \(r\) with \(r>q\), then
\[
  r\in S.
\]
Moreover, if \(r\mid\Phi_d(x)\) and \(r\nmid d\), then
\[
  \ord_r(x)=d.
\]
\end{lemma}

\begin{proof}
Since \(C\mid\sigma(x^{e_x})\mid\sigma(N)=2N\), every odd prime divisor
\(r\) of \(C\) divides \(N\), hence \(r\in S\).  If \(r\mid\Phi_d(x)\),
\(r\nmid d\), and \(r\ne x\), then the standard cyclotomic order property gives
\(\ord_r(x)=d\).  Here \(r\ne x\) because \(\Phi_d(x)\equiv1\pmod x\) for the
prime \(x\) in all cases used by the certificates.
\end{proof}

\begin{lemma}[Lower-prime cofactor refutation]
\label{lem:lower-prime-cofactor-refutation}
Let \(q=\min S\), and let \(C\mid\sigma(x^{e_x})\) be a reduced cofactor.  If
some odd prime \(\ell<q\) divides \(C\), then the branch is empty.
\end{lemma}

\begin{proof}
The divisibility \(\ell\mid C\mid\sigma(x^{e_x})\) gives
\[
  v_\ell(\sigma(x^{e_x}))>0,
\]
contradicting lower-prime avoidance in Lemma~\ref{lem:lower-prime-avoidance}.
\end{proof}

\begin{definition}[Pure row]
\label{def:pure-row}
A row is called \emph{pure} if, after removing the required \(q\)-power and
after applying all lower-prime avoidance refutations, the reduced cofactor
contributes no odd support prime larger than \(q\).  A pure row is not accepted
as closed merely because no forced prime appears.  It must be eliminated by a
separate Diophantine filter or controlled by a pure-kernel tail certificate.
\end{definition}

\begin{table}[ht]
\centering
\small
\begin{tabular}{c|l}
\toprule
branch & pure-exception mechanism used in the certificate package\\
\midrule
\(q=5\) &
parametric \(C_5(x)\)-tail and \(C_2(\pi)\)-post-window records\\
\(q=7\) &
order-three pure leaves are archive-refuted; \(E_2\) and \(E_6\) pure kernels are tail-controlled\\
\(q=11\) &
\(\Phi_5(x)=11^c\) and \(\Phi_{10}(x)=11^c\) filters; \(E_2\) pure family \(\pi=2\cdot11^{2t}-1\)\\
\(q=13\) &
\(\Phi_3(x)=13^c\) and \(\Phi_6(x)=13^c\) filters; \(E_2\) pure family \(\pi=2\cdot13^b-1\)\\
\(q=17\) &
only \(E_2\) has a pure family, \(\pi=2\cdot17^b-1\)\\
\bottomrule
\end{tabular}
\caption{Reduced cofactor and pure-exception mechanisms.}
\label{tab:pure-exceptions}
\end{table}

\begin{table}[ht]
\centering
\small
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{0.22\textwidth}
  >{\raggedright\arraybackslash}p{0.17\textwidth}
  >{\raggedright\arraybackslash}X
  >{\raggedright\arraybackslash}p{0.20\textwidth}}
\toprule
pure equation & certificate-verified solution set & method in \(\Csmall\) & branch reason for rejection\\
\midrule
\(\Phi_5(x)=11^c\) & \((x,c)=(3,2)\) &
lower-level Diophantine screen; direct substitution of the listed solution &
\(x=3<11\), impossible when \(q=11\)\\
\(\Phi_{10}(x)=11^c\) & \((x,c)=(2,1)\) &
lower-level Diophantine screen; direct substitution of the listed solution &
\(x=2\) is outside the odd \(q=11\) support\\
\(\Phi_3(x)=13^c\) & \((x,c)=(3,1)\) &
quadratic pure screen with finite exponent audit &
\(x=3<13\), impossible when \(q=13\)\\
\(\Phi_6(x)=13^c\) & \((x,c)=(4,1)\) &
quadratic pure screen with finite exponent audit &
\(x=4\) is not a support prime\\
\bottomrule
\end{tabularx}
\caption{Pure Diophantine screens used for \(q=11\) and \(q=13\).  The master
wrappers check that these lower-level screen records are present before
accepting the corresponding strict frontier closures.}
\label{tab:pure-screen-details}
\end{table}

\section{The Certificate System}
\label{sec:certificates}

The proof is finite but not purely handwritten: the branch leaves are closed by
machine-readable certificates.  The verifier contract has two layers.  The
lower layer checks arithmetic records: integer factorizations, order records,
valuation labels, pure-screen records, endpoint records, and exact rational
inequalities.  The upper layer is a master-wrapper layer: it checks that the
expected records are present, that their labels match the mathematical coverage
split, and that no release leaf remains unresolved.

In particular, the \(q=17\) verifier in \(\Csmall\) is explicitly a
master-wrapper verifier.  It verifies the frontier labels, record types,
endpoint inequalities, coverage wrapper, and the small endpoint certificates in
Table~\ref{tab:q17-endpoint-certificates}.  It should not be read as a
standalone general-purpose arithmetic verifier for arbitrary \(q=17\) data.

\begin{definition}[Certificate record families]
The certificate files use the following record families.
\[
  \texttt{branch\_archive},\quad
  \texttt{coverage\_split},\quad
  \texttt{leaf\_status},\quad
  \texttt{forced\_cofactor},
\]
\[
  \texttt{tail\_count\_certificate},\quad
  \texttt{abundance\_obstruction},\quad
  \texttt{literature\_filter\_certificate},
\]
together with the strict frontier records
\[
  \begin{array}{l}
  \texttt{strict\_q7\_forced\_or\_pure\_tail\_closure},\\
  \texttt{strict\_q11\_forced\_or\_pure\_tail\_closure},\\
  \texttt{strict\_q13\_forced\_or\_pure\_tail\_closure},\\
  \texttt{strict\_q17\_forced\_or\_pure\_tail\_closure}.
  \end{array}
\]
For \(q=5\), the final layer also uses the parametric records
\[
  \begin{array}{l}
  \texttt{parametric\_post\_window\_closure},\\
  \texttt{parametric\_q5e1\_pi\_window\_closure},\\
  \texttt{parametric\_q5n\_witness\_window\_closure}.
  \end{array}
\]
\end{definition}

\begin{definition}[Envelope tuple]
\label{def:envelope-tuple}
For a tail estimate we allow repeated lower-bound placeholders.  An
\emph{envelope tuple} is a finite tuple
\[
  K_{\rm env}=(k_1,\ldots,k_t)
\]
of primes or certified prime lower bounds, and
\[
  \Hfun(K_{\rm env})
  :=
  \prod_{i=1}^t\frac{k_i}{k_i-1}.
\]
Thus \(K_{\rm env}=(7,29,29)\) is a tuple, not a set: the two occurrences of
\(29\) represent two independent worst-case support-prime slots.
\end{definition}

\begin{lemma}[Tail envelope]
\label{lem:tail-envelope}
Let \(K_{\rm env}=(k_1,\ldots,k_t)\) be a certified envelope tuple.  Suppose a branch
certifies that all remaining support primes are at least \(B\), and that at
most \(M\) such remaining primes can occur.  If
\[
  \Hfun(K_{\rm env})\left(\frac{B}{B-1}\right)^M<2,
\]
then the branch contains no odd perfect number.
\end{lemma}

\begin{proof}
For any support set \(S\),
\[
  \frac{\sigma(N)}{N}
  =
  \prod_{p\in S}\frac{1-p^{-(e_p+1)}}{1-p^{-1}}
  <
  \prod_{p\in S}\frac{p}{p-1}
  =\Hfun(S).
\]
If \(N\) is perfect, the left side is \(2\), hence \(2<\Hfun(S)\).  Under the
branch hypotheses,
\[
  \Hfun(S)
  \le
  \Hfun(K_{\rm env})\left(\frac{B}{B-1}\right)^M
  <2,
\]
a contradiction.
\end{proof}

\begin{definition}[\texttt{tail\_count\_certificate}\((B,M)\)]
\label{def:tail-count-certificate}
A record
\[
  \texttt{tail\_count\_certificate}(B,M)
\]
certifies two branch-specific facts after the displayed envelope tuple has been
fixed:
\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item every unresolved support prime not already represented in the envelope
tuple is at least \(B\);
\item at most \(M\) such further support-prime slots remain.
\end{enumerate}
The number \(M=18\) used in the strict frontier records of \(\Csmall\) is
therefore not a universal constant.  It is release data: each strict frontier
record carries a tail-count certificate with
\[
  B=59,\qquad M=18,
\]
and the master wrapper accepts the final tail inequality only after that record
has been checked.  The proof does not require \(M=18\) to be optimal.
\end{definition}

\begin{criterion}[Master-wrapper soundness]
\label{crit:master-wrapper}
A master wrapper closes a branch when it verifies all of the following:
\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item the mathematical coverage split for the branch;
\item the presence and uniqueness of the expected terminal labels;
\item for every terminal label, one accepted refutation, forced-tail closure,
pure-tail closure, or certified child archive;
\item exact rational verification of every tail inequality;
\item no unresolved, reduced, or delegated leaf remains outside an accepted
child archive.
\end{enumerate}
\end{criterion}

\begin{table}[ht]
\centering
\small
\begin{tabular}{p{0.34\textwidth}|p{0.56\textwidth}}
\toprule
endpoint item & lower-level check in \(\Csmall\)\\
\midrule
order-\(17\) forced endpoint \(103\) &
The endpoint certificate checks that \(103\) is prime, \(103\equiv1\pmod{17}\),
and that the preceding candidates \(35,52,69,86\) in the progression
\(1\pmod{17}\) are composite.\\
Euler order-two forced endpoint \(19\) &
The frontier record uses only \(r>17\) and \(\ord_r(\pi)=2\); the least odd
prime \(>17\) is \(19\).\\
pure endpoint \(577\) in \(\pi=2\cdot17^b-1\) &
The endpoint certificate checks \(2\cdot17-1=33=3\cdot11\) and
\(2\cdot17^2-1=577\), with \(577\) prime.\\
\bottomrule
\end{tabular}
\caption{Lower-level endpoint checks used by the \(q=17\) master-wrapper
verifier.}
\label{tab:q17-endpoint-certificates}
\end{table}
\FloatBarrier

\begin{remark}[Certificate files]
The certificate files used by this paper are:
\[
\begin{array}{ll}
q=5: & \texttt{q5\_master\_bundle.jsonl},\quad
       \texttt{q5\_branch\_closure\_verifier\_strict.py},\\
q=7: & \texttt{q7\_master\_bundle.jsonl},\quad
       \texttt{q7\_branch\_closure\_verifier.py},\\
q=11: & \texttt{q11\_master\_bundle.jsonl},\quad
        \texttt{q11\_branch\_closure\_verifier.py},\\
q=13: & \texttt{q13\_master\_bundle.jsonl},\quad
        \texttt{q13\_branch\_closure\_verifier.py},\\
q=17: & \texttt{q17\_master\_bundle.jsonl},\quad
        \texttt{q17\_branch\_closure\_verifier.py}.
\end{array}
\]
The \(q=17\) master bundle records the strict frontier layer in the same
minimal format used for \(q=11\) and \(q=13\), plus the endpoint certificates
listed in Table~\ref{tab:q17-endpoint-certificates}.
\end{remark}

\begin{table}[!htbp]
\centering
\scriptsize
\setlength{\tabcolsep}{2pt}
\begin{tabularx}{\textwidth}{c l
  >{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.31\textwidth}
  >{\raggedright\arraybackslash}X}
\toprule
\(q\) & artifact & file & SHA256 & expected terminal output\\
\midrule
5 &
bundle &
\path{q5_master_bundle.jsonl} &
\shasplit{90fc8b3a1210f3397e9a6baef9c43a4cd}{7bdb347f3f418efd81ca75ec1dc62aa} &
\texttt{q=5 branch inventory exhausted}\\
 &
verifier &
\path{q5_branch_closure_verifier_strict.py} &
\shasplit{ef1dd7e0e3b3d727bd71ead4f3aebeef}{0c4db89810f4f5fcd5d60ad072cefc26} &
\\
\addlinespace
7 &
bundle &
\path{q7_master_bundle.jsonl} &
\shasplit{b49297450faef6f707044e6ad0b02e712}{d3475d1609ab2df37763f044320521d} &
\texttt{q=7 branch inventory exhausted}\\
 &
verifier &
\path{q7_branch_closure_verifier.py} &
\shasplit{2643e2747d8ff52b740a9de2141982f}{abeb53e637ff3c92cc10b589fa6157e6c} &
\\
\addlinespace
11 &
bundle &
\path{q11_master_bundle.jsonl} &
\shasplit{30ebf8c3beb98047e78419f7baaec153}{f4ceedf8a848c02ec9aaaec9127909e2} &
\texttt{q=11 branch inventory exhausted}\\
 &
verifier &
\path{q11_branch_closure_verifier.py} &
\shasplit{b66828e75a0911b5c82cc67abb5293cd}{b43e8961c3bf7c878b6c02eec16c0491} &
\\
\addlinespace
13 &
bundle &
\path{q13_master_bundle.jsonl} &
\shasplit{7e2b38f8c8e10a792a39f2bfc64db0f}{b332507b6607c9c693a04d8dbae437b22} &
\texttt{q=13 branch inventory exhausted}\\
 &
verifier &
\path{q13_branch_closure_verifier.py} &
\shasplit{1f64d79777b0b20d630a4059ea063943}{221474b541e7b013aa34bb93e9c73561} &
\\
\addlinespace
17 &
bundle &
\path{q17_master_bundle.jsonl} &
\shasplit{8619738b072708ef5379c45c2fdb1baf}{bb0d28a7f24262cbaf7b4e49d6682e4d} &
\texttt{q=17 branch inventory exhausted}\\
 &
verifier &
\path{q17_branch_closure_verifier.py} &
\shasplit{c0c1650e38c69ddba4c8911e282a6643}{0ffc71042fcb59e30bbe3d2879dc51bd} &
\\
\bottomrule
\end{tabularx}
\caption{Reproducibility table for the frozen certificate release
\(\Csmall=\CertRelease\).}
\label{tab:reproducibility-release}
\end{table}
\FloatBarrier

\begin{remark}[Ancillary Git repository]
All files in Table~\ref{tab:reproducibility-release} are included as ancillary
files and in the accompanying Git repository
\begin{center}
  \url{https://github.com/Mantovanelli1110/opn-small-prime-closure-certificates}.
\end{center}
The corresponding Git release tag is \texttt{C-small-2026-07}; the release
page is
\begin{center}
  \url{https://github.com/Mantovanelli1110/opn-small-prime-closure-certificates/releases/tag/C-small-2026-07}.
\end{center}
Running each listed verifier on the listed bundle from the repository root
produces the stated terminal output.  The exact reproduction commands are:
\begin{verbatim}
python q5_branch_closure_verifier_strict.py q5_master_bundle.jsonl
python q7_branch_closure_verifier.py q7_master_bundle.jsonl
python q11_branch_closure_verifier.py q11_master_bundle.jsonl
python q13_branch_closure_verifier.py q13_master_bundle.jsonl
python q17_branch_closure_verifier.py q17_master_bundle.jsonl
\end{verbatim}
The repository also contains the paper source, the expanded \(q=5\) detail
file, the bibliography file, a release manifest, and the local dependency
modules imported by the \(q=5\) and \(q=7\) wrapper scripts.
\end{remark}

\section{Closure of the \(q=5\) Branch}
\label{sec:q5}

The \(q=5\) branch has only one lower prime to avoid, namely \(3\).  First,
lower-prime avoidance excludes the Euler residue \(\pi\equiv2\pmod3\), because
then \(\ord_3(\pi)=2\) and \(\alpha+1\equiv2\pmod4\) would force
\[
  3\mid\sigma(\pi^\alpha).
\]
Hence every surviving \(q=5\) row has
\[
  \pi\equiv1\pmod3.
\]
In particular \(5\) itself is non-Euler.

\begin{proposition}[First \(q=5\) coverage split]
\label{prop:q5-coverage}
Every odd perfect number in the branch \(q=5\) realizes at least one of the
three children
\[
  \mathbf{Q5E2},\qquad \mathbf{Q5E1},\qquad \mathbf{Q5N},
\]
where
\[
  \mathbf{Q5E2}:\ \pi\equiv-1\pmod5,
\]
\[
  \mathbf{Q5E1}:\ \pi\equiv1\pmod5,\quad 5\mid\alpha+1,
\]
and
\[
  \mathbf{Q5N}:\ \exists p\in S,\ p\ne5,\ p\ne\pi,\quad
  p\equiv1\pmod5,\quad 5\mid e_p+1.
\]
\end{proposition}

\begin{proof}
By Lemma~\ref{lem:q-input-exists}, there is a \(5\)-input witness \(p\ne5\).
If it is non-Euler, then \(e_p+1\) is odd.  The only odd input order modulo
\(5\) is \(1\), so \(p\equiv1\pmod5\), and the order-one input condition gives
\(5\mid e_p+1\).  This is \(\mathbf{Q5N}\).

If the witness is the Euler prime, then \(\alpha+1\equiv2\pmod4\).  The
possible orders modulo \(5\) are \(1,2,4\).  Order \(4\) cannot divide
\(\alpha+1\).  Order \(1\) gives \(\pi\equiv1\pmod5\) and
\(5\mid\alpha+1\), which is \(\mathbf{Q5E1}\).  Order \(2\) gives
\(\pi\equiv-1\pmod5\), which is \(\mathbf{Q5E2}\).
\end{proof}

\begin{proposition}[Reduced \(q=5\) cofactors]
\label{prop:q5-reduced-cofactors}
The three \(q=5\) children reduce as follows.
\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item In \(\mathbf{Q5N}\) and \(\mathbf{Q5E1}\), the cofactor
\[
  C_5(x)=\frac{\Phi_5(x)}5
\]
is an integer \(>1\).  If \(3\mid C_5(x)\), the row is refuted by lower-prime
avoidance.  Otherwise \(C_5(x)\) forces a support prime \(r>5\) with
\[
  \ord_r(x)=5,\qquad r\equiv1\pmod5.
\]
\item In \(\mathbf{Q5E2}\), the cofactor
\[
  C_2(\pi)=\frac{\pi+1}{5^{v_5(\pi+1)}}
\]
is an integer \(>1\).  If \(3\mid C_2(\pi)\), the row is refuted by
lower-prime avoidance.  Otherwise it forces a support prime \(r>5\) with
\[
  \ord_r(\pi)=2.
\]
\end{enumerate}
\end{proposition}

\begin{proof}
For \(\mathbf{Q5N}\) and \(\mathbf{Q5E1}\), the source \(x\) satisfies
\(x\equiv1\pmod5\) and \(5\mid e_x+1\).  Thus \(\Phi_5(x)\mid\sigma(x^{e_x})\).
LTE gives \(v_5(\Phi_5(x))=1\), so \(C_5(x)\) is integral and not divisible by
\(5\).  Since \(x>5\), \(C_5(x)>1\).  A divisor \(3\) contradicts
lower-prime avoidance.  Any other prime divisor \(r\) is \(>5\), lies in \(S\),
and has \(\ord_r(x)=5\).

For \(\mathbf{Q5E2}\), \(\pi\equiv-1\pmod5\) and
\(\alpha+1\equiv2\pmod4\), so \(\Phi_2(\pi)=\pi+1\) divides
\(\sigma(\pi^\alpha)\).  Removing the full \(5\)-power gives \(C_2(\pi)\).
The same lower-prime and forced-prime argument applies, and a surviving odd
prime divisor \(r>5\) of \(\pi+1\) has \(\ord_r(\pi)=2\).
\end{proof}

\begin{theorem}[Closure of the \(q=5\) inventory]
\label{thm:q5-closed}
Relative to the certificate release \(\Csmall\), the \(q=5\) branch inventory is
exhausted.
\end{theorem}

\begin{proof}
By Proposition~\ref{prop:q5-coverage}, every realization of the \(q=5\) branch
lies in at least one of \(\mathbf{Q5E2}\), \(\mathbf{Q5E1}\), and
\(\mathbf{Q5N}\).

The certificate package closes \(\mathbf{Q5E2}\) by finite successor archives
for the four post-window pairs
\[
  (109,11),\quad (229,23),\quad (349,7),\quad (409,41),
\]
together with parametric post-window records.  It closes \(\mathbf{Q5E1}\) by
the exact finite Euler-prime window
\[
  \pi<1381,\qquad \pi\equiv1\pmod{60},
\]
and a parametric \(C_5(\pi)\)-tail record for \(\pi\ge1381\).  It closes
\(\mathbf{Q5N}\) by the exact finite witness-prime window
\[
  p<211,\qquad p\equiv1\pmod5,
\]
and a parametric \(C_5(p)\)-tail record for \(p\ge211\).

The strict wrapper verifies these dependencies and prints the terminal summary
\[
\begin{gathered}
  \mathtt{Q5E2\ closed},\qquad
  \mathtt{Q5E1\ closed},\qquad
  \mathtt{Q5N\ closed},\\
  \mathtt{q=5\ branch\ inventory\ exhausted}.
\end{gathered}
\]
Thus no certified leaf remains in any child, and the three children cover the
parent branch.
\end{proof}

\section{Expanded \(q=5\) Derivation}
\label{sec:q5-expanded-derivation}

The preceding section gives the compressed branch proof.  For readability and
auditability, this section includes the fuller \(q=5\) derivation.  This is the
didactic branch: it shows in detail how lower-prime avoidance, the first
\(5\)-input split, second-level cofactors, finite successor windows, and
parametric tail records fit together before the same forced-or-pure pattern is
reused for \(q=7,11,13,17\).

\input{arxiv_q5_expanded_detail.tex}

\section{Closure of the \(q=7\) Branch}
\label{sec:q7}

For \(q=7\), lower-prime avoidance applies to \(3\) and \(5\).  The first
coverage split consists of six children:
\[
  \mathbf{Q7N1},\quad \mathbf{Q7N3},\quad
  \mathbf{Q7E1},\quad \mathbf{Q7E2},\quad
  \mathbf{Q7E3},\quad \mathbf{Q7E6}.
\]
This is exactly Table~\ref{tab:first-input-labels} for \(q=7\).

\begin{proposition}[Reduced \(q=7\) frontier]
\label{prop:q7-frontier}
After lower-prime avoidance, the six \(q=7\) leaves have the strict
forced-or-pure frontier recorded in Table~\ref{tab:q7-frontier}.
\end{proposition}

\begin{table}[ht]
\centering
\small
\begin{tabular}{c|c|c|c}
\toprule
leaf & cofactor & envelope tuple used & mode\\
\midrule
\(\mathbf{Q7N1}\) & \(\Phi_7(p)/7\) & \((7,29,29)\) & forced\\
\(\mathbf{Q7N3}\) & \(\Phi_3(p)/7^{v_7}\) & \((7,11,13)\) & forced; pure archive-refuted\\
\(\mathbf{Q7E1}\) & \(\Phi_7(\pi)/7\) & \((7,29,29)\) & forced\\
\(\mathbf{Q7E2}\) & \((\pi+1)/7^{v_7}\) & \((7,13,11)\), pure \((7,13)\) & forced or pure\\
\(\mathbf{Q7E3}\) & \(\Phi_3(\pi)/7^{v_7}\) & \((7,37,13)\) & forced; pure archive-refuted\\
\(\mathbf{Q7E6}\) & \(\Phi_6(\pi)/7^{v_7}\) & \((7,17,13)\), pure \((7,17)\) & forced or pure\\
\bottomrule
\end{tabular}
\caption{Strict \(q=7\) frontier layer.  Each listed envelope tuple satisfies the
tail inequality with \(B=59\) and \(M=18\).}
\label{tab:q7-frontier}
\end{table}
\FloatBarrier

\begin{proof}
The cofactor statements follow from Lemmas~\ref{lem:forced-prime-alternative}
and \ref{lem:lower-prime-cofactor-refutation}.  For example, in
\(\mathbf{Q7N1}\) the order-one source \(p\equiv1\pmod7\) gives
\(\Phi_7(p)/7>1\), not divisible by \(7\); after excluding lower divisors
\(3,5\), a surviving divisor is \(r>7\) with \(\ord_r(p)=7\), hence
\(r\equiv1\pmod7\).  The certificate records the least admissible source and
forced-prime lower bounds as the envelope tuple \(K_{\rm env}=(7,29,29)\).
The other rows are
identical applications of the same reduced-cofactor rule, with the pure rows
handled by the pure-exception entries displayed in the table.
\end{proof}

\begin{theorem}[Closure of the \(q=7\) inventory]
\label{thm:q7-closed}
Relative to the certificate release \(\Csmall\), the \(q=7\) branch inventory is
exhausted.
\end{theorem}

\begin{proof}
The six leaves in Table~\ref{tab:q7-frontier} cover the \(q=7\) branch by
Proposition~\ref{prop:general-coverage-split}.  The strict \(q=7\) verifier
checks each leaf, the lower-prime alternatives, and the exact inequalities
\[
  \Hfun(K_{\rm env})\left(\frac{59}{58}\right)^{18}<2
\]
for the envelope tuples in Table~\ref{tab:q7-frontier}.  By
Lemma~\ref{lem:tail-envelope}, each accepted forced or pure envelope tuple excludes
the corresponding tail.  The wrapper verifies all six frontier records and
prints
\[
  \mathtt{Q7\ forced/pure\ frontier\ closures\ verified:\ 6/6},
\]
followed by
\[
  \mathtt{q=7\ branch\ inventory\ exhausted}.
\]
Thus every child in the complete \(q=7\) coverage split is closed.
\end{proof}

\section{Closure of the \(q=11\) Branch}
\label{sec:q11}

For \(q=11\), lower-prime avoidance applies to \(3,5,7\), and the active
support floor is \(\omega(N)\ge27\).  The first-input coverage split has six
children:
\[
  \mathbf{Q11N1},\quad \mathbf{Q11N5},\quad
  \mathbf{Q11E1},\quad \mathbf{Q11E2},\quad
  \mathbf{Q11E5},\quad \mathbf{Q11E10}.
\]

\begin{table}[ht]
\centering
\small
\begin{tabularx}{\textwidth}{c|>{\raggedright\arraybackslash}X|c|>{\raggedright\arraybackslash}p{0.23\textwidth}}
\toprule
leaf & cofactor & endpoint kernel & pure status\\
\midrule
\(\mathbf{Q11N1}\) & \(\Phi_{11}(p)/11\) & \(\{11,23\}\) & none\\
\(\mathbf{Q11N5}\) & \(\Phi_5(p)/11^{v_{11}(\Phi_5(p))}\) & \(\{11,31\}\) & \(\Phi_5(x)=11^c\) refuted\\
\(\mathbf{Q11E1}\) & \(\Phi_{11}(\pi)/11\) & \(\{11,23\}\) & none\\
\(\mathbf{Q11E2}\) & \((\pi+1)/11^{v_{11}(\pi+1)}\) & \(\{11,13\}\), pure \(\{11,241\}\) & tail-controlled\\
\(\mathbf{Q11E5}\) & \(\Phi_5(\pi)/11^{v_{11}(\Phi_5(\pi))}\) & \(\{11,31\}\) & \(\Phi_5(x)=11^c\) refuted\\
\(\mathbf{Q11E10}\) & \(\Phi_{10}(\pi)/11^{v_{11}(\Phi_{10}(\pi))}\) & \(\{11,31\}\) & \(\Phi_{10}(x)=11^c\) refuted\\
\bottomrule
\end{tabularx}
\caption{Strict \(q=11\) frontier layer, with \(B=59\) and \(M=18\).}
\label{tab:q11-frontier}
\end{table}
\FloatBarrier

\begin{proposition}[Pure exceptions for \(q=11\)]
\label{prop:q11-pure}
The only pure exceptions in the \(q=11\) frontier are the following:
\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item \(\Phi_5(x)=11^c\), whose certificate-verified positive solution set is
\(\{(3,2)\}\), impossible in the branch \(q=11\);
\item the Euler order-two pure family
\[
  \pi=2\cdot 11^{2t}-1,\qquad t\ge1,
\]
whose first prime endpoint is \(\pi=241\) and whose pure kernel satisfies
\[
  \Hfun(\{11,241\})\left(\frac{59}{58}\right)^{18}<2;
\]
\item \(\Phi_{10}(x)=11^c\), whose certificate-verified positive solution set is
\(\{(2,1)\}\), impossible in an odd \(q=11\) support branch.
\end{enumerate}
\end{proposition}

\begin{proof}
These are the three pure-dependency records in
\(\texttt{q11\_master\_bundle.jsonl}\).  The first and third are Diophantine
filters: their certificate-verified solutions lie below the minimal prime or outside the
odd support.  The second is not refuted algebraically; it is accepted only
after the exact pure-kernel tail inequality is checked.  By
Lemma~\ref{lem:tail-envelope}, that inequality closes the pure family.
\end{proof}

\begin{theorem}[Closure of the \(q=11\) inventory]
\label{thm:q11-closed}
Relative to the certificate release \(\Csmall\), the \(q=11\) branch inventory is
exhausted.
\end{theorem}

\begin{proof}
The six leaves in Table~\ref{tab:q11-frontier} cover the \(q=11\) branch by
Proposition~\ref{prop:general-coverage-split}.  The strict verifier checks the
forced endpoint inequalities for
\[
  \{11,23\},\quad \{11,31\},\quad \{11,13\},
\]
and the pure endpoint \(\{11,241\}\), all with \(B=59,M=18\).  It also checks
the pure-dependency set described in Proposition~\ref{prop:q11-pure}.  The
verified terminal output is
\[
  \mathtt{Q11\ strict\ frontier\ closures\ verified:\ 6/6}
\]
and
\[
  \mathtt{q=11\ branch\ inventory\ exhausted}.
\]
Therefore all children in the complete \(q=11\) split are closed.
\end{proof}

\section{Closure of the \(q=13\) Branch}
\label{sec:q13}

For \(q=13\), lower-prime avoidance applies to \(3,5,7,11\).  The first-input
coverage split has the six children
\[
  \mathbf{Q13N1},\quad \mathbf{Q13N3},\quad
  \mathbf{Q13E1},\quad \mathbf{Q13E2},\quad
  \mathbf{Q13E3},\quad \mathbf{Q13E6}.
\]

\begin{table}[ht]
\centering
\small
\begin{tabularx}{\textwidth}{c|>{\raggedright\arraybackslash}X|c|>{\raggedright\arraybackslash}p{0.23\textwidth}}
\toprule
leaf & cofactor & endpoint kernel & pure status\\
\midrule
\(\mathbf{Q13N1}\) & \(\Phi_{13}(p)/13\) & \(\{13,53\}\) & none\\
\(\mathbf{Q13N3}\) & \(\Phi_3(p)/13^{v_{13}(\Phi_3(p))}\) & \(\{13,19\}\) & \(\Phi_3(x)=13^c\) refuted\\
\(\mathbf{Q13E1}\) & \(\Phi_{13}(\pi)/13\) & \(\{13,53\}\) & none\\
\(\mathbf{Q13E2}\) & \((\pi+1)/13^{v_{13}(\pi+1)}\) & \(\{13,17\}\), pure \(\{13,337\}\) & tail-controlled\\
\(\mathbf{Q13E3}\) & \(\Phi_3(\pi)/13^{v_{13}(\Phi_3(\pi))}\) & \(\{13,19\}\) & \(\Phi_3(x)=13^c\) refuted\\
\(\mathbf{Q13E6}\) & \(\Phi_6(\pi)/13^{v_{13}(\Phi_6(\pi))}\) & \(\{13,19\}\) & \(\Phi_6(x)=13^c\) refuted\\
\bottomrule
\end{tabularx}
\caption{Strict \(q=13\) frontier layer, with \(B=59\) and \(M=18\).}
\label{tab:q13-frontier}
\end{table}

\begin{proposition}[Pure exceptions for \(q=13\)]
\label{prop:q13-pure}
The \(q=13\) pure screen consists of:
\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item \(\Phi_3(x)=13^c\), whose certificate-verified positive solution set is
\(\{(3,1)\}\),
impossible in the \(q=13\) branch;
\item the Euler order-two pure family
\[
  \pi=2\cdot13^b-1,\qquad b\ge1,
\]
whose first prime endpoint is \(337\), with
\[
  \Hfun(\{13,337\})\left(\frac{59}{58}\right)^{18}<2;
\]
\item \(\Phi_6(\pi)=13^c\), whose certificate-verified positive solution set is
\(\{(4,1)\}\),
not a prime.
\end{enumerate}
\end{proposition}

\begin{proof}
These are the pure-dependency records in the \(q=13\) master bundle.  The two
quadratic pure equations are eliminated by their certificate-verified solution sets and the
branch hypotheses.  The order-two family is closed by the pure-kernel
inequality and Lemma~\ref{lem:tail-envelope}.
\end{proof}

\begin{theorem}[Closure of the \(q=13\) inventory]
\label{thm:q13-closed}
Relative to the certificate release \(\Csmall\), the \(q=13\) branch inventory is
exhausted.
\end{theorem}

\begin{proof}
The six leaves in Table~\ref{tab:q13-frontier} cover the branch by
Proposition~\ref{prop:general-coverage-split}.  The strict verifier checks the
forced endpoint inequalities for
\[
  \{13,53\},\quad \{13,19\},\quad \{13,17\},
\]
and the pure endpoint \(\{13,337\}\).  It also checks the three pure
dependencies of Proposition~\ref{prop:q13-pure}.  The terminal output is
\[
  \mathtt{Q13\ strict\ frontier\ closures\ verified:\ 6/6}
\]
and
\[
  \mathtt{q=13\ branch\ inventory\ exhausted}.
\]
Hence every child of the complete \(q=13\) coverage split is closed.
\end{proof}

\section{Closure of the \(q=17\) Branch}
\label{sec:q17}

For \(q=17\), lower-prime avoidance applies to
\[
  3,\ 5,\ 7,\ 11,\ 13.
\]
The possible first-input children are
\[
  \mathbf{Q17N1},\qquad \mathbf{Q17E1},\qquad \mathbf{Q17E2}.
\]
Indeed, the only odd divisor of \(16\) is \(1\), and the Euler exponent permits
only orders \(1\) and \(2\).

\begin{proposition}[Reduced \(q=17\) frontier]
\label{prop:q17-frontier}
The strict \(q=17\) frontier consists of:
\[
\begin{array}{c|c|c}
\text{leaf} & \text{cofactor} & \text{endpoint kernel}\\
\hline
\mathbf{Q17N1} & \Phi_{17}(p)/17 & \{17,103\}\\
\mathbf{Q17E1} & \Phi_{17}(\pi)/17 & \{17,103\}\\
\mathbf{Q17E2} & (\pi+1)/17^{v_{17}(\pi+1)} & \{17,19\},\ \text{pure }\{17,577\}.
\end{array}
\]
All endpoints use \(B=59\) and \(M=18\).
\end{proposition}

\begin{proof}
In the order-one leaves, the source \(x\) satisfies \(x\equiv1\pmod{17}\) and
the relevant exponent parameter is divisible by \(17\).  Thus
\(\Phi_{17}(x)\mid\sigma(x^{e_x})\), and LTE gives
\[
  v_{17}(\Phi_{17}(x))=1.
\]
Hence \(C_{17}(x)=\Phi_{17}(x)/17\) is an integer \(>1\), not divisible by
\(17\).  After lower-prime avoidance, any surviving prime divisor \(r\) is
\(>17\) and has \(\ord_r(x)=17\), so \(r\equiv1\pmod{17}\).  The first
admissible endpoint used by the certificate is \(r=103\).

In the Euler order-two leaf, \(\pi\equiv-1\pmod{17}\) and
\(\alpha+1\equiv2\pmod4\), so \(\pi+1\mid\sigma(\pi^\alpha)\).  After removing
the \(17\)-part, any surviving odd divisor \(r>17\) has \(\ord_r(\pi)=2\), and
the worst endpoint is \(r=19\).  If no such odd divisor remains, the reduced
cofactor is a power of \(2\), giving the pure family
\[
  \pi=2\cdot17^b-1.
\]
The first prime endpoint in this family is \(577\), which is the pure kernel
recorded in the master bundle.
\end{proof}

\begin{theorem}[Closure of the \(q=17\) inventory]
\label{thm:q17-closed}
Relative to the certificate release \(\Csmall\), the \(q=17\) branch inventory is
exhausted.
\end{theorem}

\begin{proof}
The three leaves \(\mathbf{Q17N1},\mathbf{Q17E1},\mathbf{Q17E2}\) cover the
\(q=17\) branch by Proposition~\ref{prop:general-coverage-split}.  The strict
verifier checks
\[
  \Hfun(\{17,103\})\left(\frac{59}{58}\right)^{18}<2,
\]
\[
  \Hfun(\{17,19\})\left(\frac{59}{58}\right)^{18}<2,
\]
and
\[
  \Hfun(\{17,577\})\left(\frac{59}{58}\right)^{18}<2.
\]
By Lemma~\ref{lem:tail-envelope}, these inequalities close respectively the
order-one forced rows, the Euler order-two forced row, and the Euler order-two
pure family.  The master wrapper verifies all three strict frontier records and
prints
\[
  \mathtt{Q17\ strict\ frontier\ closures\ verified:\ 3/3},
\]
followed by
\[
  \mathtt{q=17\ branch\ inventory\ exhausted}.
\]
Thus every child in the complete \(q=17\) split is closed.
\end{proof}

\section{Final Branch-Closure Statement}
\label{sec:final}

\begin{theorem}[Certified closure for \(q=5,7,11,13,17\)]
\label{thm:final-closure}
Relative to the explicitly listed verifier contract and certificate release
\(\Csmall\), there is no odd perfect number \(N\) with
\(\min\{p:p\mid N\}\in\{5,7,11,13,17\}\).  Equivalently, the certified branch
inventories for \(q=5,7,11,13,17\) are exhausted.
\end{theorem}

\begin{proof}
Theorem~\ref{thm:q5-closed}, equivalently the detailed
Theorem~\ref{thm:q5-current-branch-inventory-closed}, closes \(q=5\).
Theorem~\ref{thm:q7-closed} closes \(q=7\).
Theorem~\ref{thm:q11-closed} closes \(q=11\).  Theorem~\ref{thm:q13-closed}
closes \(q=13\).  Theorem~\ref{thm:q17-closed} closes \(q=17\).
These are minimal-prime branch statements in the sense of
Definition~\ref{def:minimal-prime-branch}; by Remark~\ref{rem:scope-warning}
they do not claim anything about numbers divisible by one of these primes but
also divisible by a smaller prime.  Combining the five branch theorems gives
the displayed final statement.
\end{proof}

\begin{remark}[Remaining branches]
The closure theorem leaves two tasks outside the scope of this paper: \(q=3\)
and \(q\ge19\).
The branch \(q=3\) has no lower-prime avoidance constraints.  The residual
branch \(q\ge19\) requires a separate treatment of the order types for the
first \(q\)-adic input primes and should not be conflated with the small-branch
certificates proved here.
\end{remark}

\section*{Acknowledgements}

ChatGPT 5.5 (OpenAI) was used for assistance with LaTeX formatting,
language refinement, literature search, proof presentation, and coding support.
The mathematical content, including all results, proofs, computations, and
conjectures, remains the sole responsibility of the author.

\nocite{*}
\FloatBarrier
\bibliographystyle{alpha}
\bibliography{references}

\end{document}
